\begin{abstract}
This paper presents a new system, called BGPmon, for monitoring the Border Gateway Protocol (BGP).  BGP is the routing protocol for the global Internet.  
Monitoring BGP is important for both operations and research; a number of public and private BGP monitors are deployed and widely used.  
%Most monitors use open source routing toolkits to capture and log updates.  
%However, the routing toolkits add unnecessary complexity to the monitor by implementing routing polices, storing RIB tables, forwarding packets and so forth.   Furthermore, most routing toolkits do not easily facilitate real-time access, do not scale to vast numbers of peers, and are not easily extended.
These existing monitors typically collect data using a full implementation of a BGP router. In contrast, BGPmon eliminates the unnecessary functions of route selection and data forwarding to focus solely on the monitoring function.   
BGPmon uses a publish/subscribe overlay network to provide real-time access to vast numbers of peers and clients. 
%Using features such as route refresh, 
All routing events are consolidated into a single XML stream.  
XML allows us to add additional features such as labeling updates to allow easy identification of useful data by clients.  
Clients subscribe to BGPmon and receive the XML stream, performing tasks such as archiving, filtering, or real-time data analysis.  
BGPmon enables scalable real-time monitoring data distribution by allowing monitors to peer with each other and form an overlay network to provide new services and features without modifying the monitors.  
\end{abstract}
